---
title: "TASK2"
author: "MW"
date: "5/19/2020"
output: html_document
---

Summary of the statistics concerning the players’ entire career.

Description: Summary of statistics.
```{r,echo=FALSE}
library(knitr)
library(ISLR)
attach(Hitters)
summary(Hitters)
```

Scatter plot with the players' salaries in relation to the number of runs.

Description: First panel shows E divison, second shows W division. 
```{r,echo=FALSE}
library(ggplot2)
par(mfrow=c(1,2))

g <- ggplot(Hitters, aes(x=Salary, y=Runs)) + geom_point(aes(col=League),na.rm=TRUE)
g+facet_grid(Hitters$Division)
```

The 2x2 table summarising the number of players in the leagues and divisions.

Decription: E,W - divisions.
A,N - leagues
```{r,echo=FALSE}
library(knitr)
m <- aggregate(Hitters[,15], by=list(League), FUN=summary)
kable(as.matrix(m))
```

Mean salaries in the two leagues, calculated using a grouping function.

Description: None
```{r,echo=FALSE}
library(knitr)
means <- aggregate(Hitters$Salary, list(League), FUN=mean, na.rm=TRUE) 
kable(as.matrix(means))
```
